Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-27 draft/ms_v5.tex
Introduction

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.  
    These efforts will soon be replaced with even more ambitious programs such as the 
    Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. 
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of
    etendue\footnote{The collecting area multiplied by the field of view.}. 
    Surveys such as HSC, and other to follow, will provide stringent constraints on 
    the cosmological model, characterize the evolution of galaxies, map out the 
    stellar structure of our Milky Way, and are poised to discover a large number of
    interesting transient objects.

    %% Challenges
    Before we can tackle outstanding scientific questions, we must first learn
    how to handle the the large amounts of data\footnote{Right now, SSP has 
    accumulated ${\sim}300$ TB of data products.} generated by these projects while 
    satisfying strict requirements for high quality image processing with accurate 
    measurement for the magnitudes and shapes of stars and galaxies. 
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys am we aim to characterize and account for subtle effects related to 
    charge-coupled devices (CCDs). 
    Cameras are made up of multiple CCDs, each with slightly different
    characteristics, and have large fields-of-views (FoV) over focal planes that 
    are not perfectly flat. 
    During observations, the seeing and background conditions display spatial and 
    temporal variations across the FoV. 
    The full-depletion, thick CCDs selected for HSC enable long exposure
    times and have excellent red-sensitivity, but they also suffer from the
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. 
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}). 
    Furthermore, as surveys reach to increasingly deeper detection limits
    (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
    ${\sim}26.4$ mag), the number of objects per unit area increases.  
    Hence, deep surveys become more sensitive and subject to the effects of blending.  
    The challenge of modern imaging surveys call for  photometric measurement methods
    that are more powerful and precise than those used in previous, shallower surveys.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the main steps involved in using \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        synthetic objects into single-frame images. 
        Below the blue box, we show an HSC image before and after the insertion of 
        synthetic galaxies. 
        The positions of synthetic objects are highlighted with green circles. 
        Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. 
        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
        On the right hand side, we show the spatial relation between \texttt{Tracts},
        \texttt{Patches}, and \texttt{Visits}. 
        The red colored box corresponds to one \texttt{Tract} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \texttt{Visits} (also commonly known as "pointings") 
        with small rectangles representing CCDs. 
        \texttt{Patches} are represented by black dashed lines. 
        One \texttt{Tract} typically contains 81 \texttt{Patches}.
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \bibitem[Antilogus et al.(2014)]{2014JInst...9C3048A} Antilogus, P., Astier, P.,
             Doherty, P., Guyonnet, A., \& Regnault, N.\ 2014, Journal of
             Instrumentation, 9, C03048

@@

@@

>>>>

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.  
    These efforts will soon be replaced with even more ambitious programs such as the 
    Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012, 
    Spergel2015})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. 
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of
    etendue\footnote{The collecting area multiplied by the field of view.}. 
    Surveys such as HSC, and other to follow, will provide stringent constraints on 
    the cosmological model, characterize the evolution of galaxies, map out the 
    stellar structure of our Milky Way, and are poised to discover a large number of
    interesting transient objects.

    %% Challenges
    Before we can tackle outstanding scientific questions, we must first learn
    how to handle the the large amounts of data\footnote{Until Feb 2017, SSP has 
    accumulated ${\sim}300$ TB of data products.} generated by these projects while 
    satisfying strict requirements for high quality image processing with accurate 
    measurement for the magnitudes and shapes of stars and galaxies. 
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys am we aim to characterize and account for subtle effects related to 
    charge-coupled devices (CCDs). 
    Cameras are made up of multiple CCDs, each with slightly different
    characteristics, and have large fields-of-views (FoV) over focal planes that 
    are not perfectly flat. 
    During observations, the seeing and background conditions display spatial and 
    temporal variations across the FoV. 
    The full-depletion, thick CCDs selected for HSC enable long exposure
    times and have excellent red-sensitivity, but they also suffer from the
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014, Guyonnet2015}), 
    which means that brighter stars have larger Point Spread Functions (PSFs) than 
    fainter stars. 
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}). 
    Furthermore, as surveys reach to increasingly deeper detection limits
    (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
    ${\sim}26.4$ mag in $i$-band), the number of objects per unit area increases.  
    Hence, deep surveys become more sensitive and subject to the effects of blending.  
    The challenge of modern imaging surveys call for  photometric measurement methods
    that are more powerful and precise than those used in previous, shallower surveys.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the workflow of \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        synthetic objects into single-frame images. 
        Below the blue box, we show an HSC image before and after the insertion of 
        synthetic galaxies. 
        The positions of synthetic objects are highlighted with green circles. 
        Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. 
        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
        On the right hand side, we show the spatial relation between \texttt{tracts},
        \texttt{patches}, and \texttt{visits}. 
        The red colored box corresponds to one \texttt{tract} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \texttt{visits} (also commonly known as "pointings") 
        with small rectangles representing CCDs. 
        \texttt{patches} are represented by black dashed lines. 
        One \texttt{tract} typically contains 81 \texttt{patches}.
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \bibitem[Antilogus et al.(2014)]{Antilogus2014} Antilogus, P., Astier, P.,
             Doherty, P., Guyonnet, A., \& Regnault, N.\ 2014, Journal of
             Instrumentation, 9, C03048

@@

    \bibitem[Guyonnet et al.(2015)]{Guyonnet2015} Guyonnet, A., Astier, P., Antilogus, 
             P., Regnault, N., \& Doherty, P.\ 2015, \aap, 575, A41

@@

    \bibitem[Spergel et al.(2015)]{Spergel2015} Spergel, D., Gehrels, N., Baltay, 
             C., et al.\ 2015, arXiv:1503.03757
